I hardly ever imagine the moment of completing my graduate studies, but here I am. 
I would not have make it this far without the invaluable and generous help and support from various 
individuals, including my supervisor, colleagues, friends and family.

I would like to express my deepest gratitude to my advisor, Dr. Abhay Deshpande
for his unwavering support throughout my Ph.D. studies, his meticulous care for me 
and his thoughtful guidance in my academic and research journey.

I still remember my first meeting with Abhay in the small garden during a Friday social.
That was my first month at Stony Brook and I was even not very fluent in English.
Abhay warmly introduced his research and invited me to talk to him later, that 
was how I knew him and joined his group for my Ph.D. study. Obviously, he is super busy 
that I was first working with KK and then Ciprian, and finally Abhay himself. 
That does not mean he is neglecting his students. Actually, you can ask for 
his suggestions or helps whenever he is available, that is also what he always 
encourages us to do and what I would urge you to do, whenever you have a chance to talk to him.

I would like to extend my sincere thanks to Dr. Ciprian Gal, for his 
invaluable guidance and support in the PREX-II/CREX experiments. His expertise 
and advice regarding research have been instrumental in shaping my studies. 
Additionally, I am truly thankful for his assistance in various aspects of my work.
I want to extend my thanks to Dr. Sanghwa Park for her help during the experiment
and the contamination analysis afterward. It is highly beneficial to
work with them.

I would like to thank Dr. Krishna Kumar, Dr. Kent Paschke, Dr. Paul King
and all the other spokespersons of the PREX-II/CREX Collaboration. It is a great honor
to be part of the collaboration. I am also grateful to every hard working postdoc and
graduate student, especially the SBU group, including Dr. Chandan Ghost, Tao Ye, Cameron 
Clarke, and Ryan Richard. Thank you for making the measurements high-precision.

I also want to thank my friends and colleagues here at Stony Brook and those in Newport News. 
The fun time with you is an indispensable supplement to the research.

Last but not least, I would like to thank my parents, sister and relatives.
Although I have not been able to meet them in person due to Covid, 
I can feel their presence around me, 
providing me with reliable support. Thank you so much!
